---
title: "Trying to Illustrate the Cool Stuff"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.height = 9)
```

The purpose of this document is to illustrate all the dynamics and functionality of this model that makes it so cool and useful. Chapter 2 will deal with all things specific to pinniped-salmon dynamics, politics, and management. Chapter 1 is just focusing on this sweet-as tool and what it can do. 

## Mayonnaise Version

This version of the model run features no social learning (by setting max receptivity height = 0), and no specialist behaviors (all steps, learning rates = 0.15; all x_base = 0.01). Boring.

```{r mayonnaise}
## Run it Manually

case.study <- "Base"
run_count <- 3
# case.study <- "N1"
# case.study <- "B1"

# bounds <- "Made-Up"
# bounds <- "High Consumption"
bounds <- "Low Consumption"

# 01 Set-Up Functions
source("ParameterManipulations/loadLoopFunctions1.R")
# 02 Prep Salmon Data
source("CopyOfRunTheModel/Prep_Bioenergetics.R")
source("CopyOfRunTheModel/Prep_Salmon_Data.R")
# 03 Prep Pinniped Data
source("CopyOfRunTheModel/Prep_Pinniped_Data.R")
# 04 Set Pars
source("CopyOfRunTheModel/set_pars.R")

# fix pars
base_x_sl <- base_x
base_x_spec <- base_x
rec_y_pars <- tibble(height = 0, width = 6)
rec_x_pars <- tibble(height = 0, width = 4.5)

# 05 Initialize Variables
source("CopyOfRunTheModel/initialize_variables.R")
# 06 Loop Functions
source("ParameterManipulations/loadLoopFunctions2.R")
# 07 Run The Loop
source("ParameterManipulations/runLoop.R")
# 08 Plots
source("Functions/Plots_Pv.R")
source("Functions/Plots_salmon.R")

plot_seals / plot_ej / plot_zc + plot_layout(axis_titles = "collect")

plot_x/plot_x_zc/plot_x_ej + plot_layout(axis_titles = "collect")
```
In this run, it takes all three species a while to learn about the Gauntlet as a foraging location. The baseline probability that any of them discover the Gauntlet is low (0.01) and they don't learn from each other, so it takes a long time for this behavior to catch on. 

## Fry Sauce

This version of the model adds specialists to the Harbor seal population and lets the sea lion x_base also be larger. Still no social learning though. No pizzazzz.

```{r fry sauce}

case.study <- "Base"
run_count <- 3
bounds <- "Low Consumption"

# 01 Set-Up Functions
source("ParameterManipulations/loadLoopFunctions1.R")
# 02 Prep Salmon Data
source("CopyOfRunTheModel/Prep_Salmon_Data.R")
# 03 Prep Pinniped Data
source("CopyOfRunTheModel/Prep_Pinniped_Data.R")
# 04 Set Pars
source("CopyOfRunTheModel/set_pars.R")

# fix pars
rec_y_pars <- tibble(height = 0, width = 6)
rec_x_pars <- tibble(height = 0, width = 4.5)

# 05 Initialize Variables
source("CopyOfRunTheModel/initialize_variables.R")
# 06 Loop Functions
source("ParameterManipulations/loadLoopFunctions2.R")
# 07 Run The Loop
source("ParameterManipulations/runLoop.R")
# 08 Plots
source("Functions/Plots_Pv.R")
source("Functions/Plots_salmon.R")

plot_seals / plot_ej / plot_zc + plot_layout(axis_titles = "collect")

plot_x/plot_x_zc/plot_x_ej + plot_layout(axis_titles = "collect")
```

The sea lions are hugely impacted and their attendance at the Gauntlet goes way up. The seals somehow learn to leave the Gauntlet faster, which is confusing...

## Garlic Aioli

This version of the model keeps specialists to the Harbor seal population and lets the sea lion x_base also be larger. And adds social learning so max receptivity is 0.5 composite.

```{r garlic aioli}

case.study <- "Base"
run_count <- 3
bounds <- "Low Consumption"

# 01 Set-Up Functions
source("ParameterManipulations/loadLoopFunctions1.R")
# 02 Prep Salmon Data
source("CopyOfRunTheModel/Prep_Salmon_Data.R")
# 03 Prep Pinniped Data
source("CopyOfRunTheModel/Prep_Pinniped_Data.R")
# 04 Set Pars
source("CopyOfRunTheModel/set_pars.R")

# fix pars
rec_y_pars <- tibble(height = sqrt(0.5), width = 6)
rec_x_pars <- tibble(height = sqrt(0.5), width = 4.5)

# 05 Initialize Variables
source("CopyOfRunTheModel/initialize_variables.R")
# 06 Loop Functions
source("ParameterManipulations/loadLoopFunctions2.R")
# 07 Run The Loop
source("ParameterManipulations/runLoop.R")
# 08 Plots
source("Functions/Plots_Pv.R")
source("Functions/Plots_salmon.R")

plot_seals / plot_ej / plot_zc + plot_layout(axis_titles = "collect")

plot_x/plot_x_zc/plot_x_ej + plot_layout(axis_titles = "collect")
```

Sea lions surprisingly aren't that impacted by this, but seals are hugely impacted. Their attendance more than doubles and they learn to leave the gauntlet faster. 