---
title: "Tuning to make sure this actually works?"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.height = 8)
```

This doc is to record all the things I try while trying to get the pinniped attendance at the Gauntlet at the right level given all the new dynamics we've added/adjusted/trashed.

## Describing the State of Things

X and Y both range from 0 to 1 but are governed by different processes that represent two separate axes of behavior. X governs learning associated with the fitness of food patch options, and Y tracks the learning associated with fear of predation (or harvest in this case). 

Whatever I'll come back here later...


## Tuning Pinniped Attendance at the Gauntlet

In this first parameterization, not enough pinnipeds are choosing to go to the Gauntlet.

```{r}
source("CopyOfRunTheModel/Run_The_Model.R")

kable(pinnipeds)
kable(data.frame(step[1], step_spec, w, w_sealion, scenario, scenario_sealion))
gauntlet_plot / plot_seals / plot_probs + plot_layout(guides = "collect", axis_titles = "collect_x")
```

In this first parameterization, not enough pinnipeds are choosing to go to the Gauntlet.
